How to publish in Biological Sciences: a guide for the uninitiated

### 2022-09-09 00-author.Rmd
with logo in yml

John Measey is Associate Professor of Biological Sciences at Stellenbosch University. He has authored or co-authored more than 200 peer reviewed scientific papers and book chapters, and five books. He has been the Editor-in-Chief of an ISI journal for 9 years, and currently serves as Associate Editor for 4 other journals. He has graduated more than 20 postgraduate students, and his blog on writing and publishing in biological sciences is read by thousands globally. British born and educated, he lives and works in the beautiful Western Cape, South Africa.

@@

>>>>

John Measey is Associate Professor of Biological Sciences at Stellenbosch University. He has authored or co-authored more than 200 peer reviewed scientific papers and book chapters, and five books. He has been the Editor-in-Chief of an ISI journal for 9 years, and currently serves as Associate Editor for 4 other journals. He has graduated more than 20 postgraduate students, and [his blog](john.measey.com/blog) on writing and publishing in biological sciences is read by thousands globally. British born and educated, he lives and works in the beautiful Western Cape, South Africa.

@@

## How to cite {-}
Measey, J. (2022) _How to publish in Biological Sciences: a guide for the uninitiated_. CRC Press, Boca Raton. 294pp. ISBN: 9781032116419  [https://doi.org/10.1201/9781003212560](https://doi.org/10.1201/9781003212560)
